Instruction

### 2018-12-26 script/Rmd/instruction.Rmd
Rewrite for a html file

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.pos = 'h', fig.align = 'center')
# Install and load packages
if (!require("rmarkdown")) {install.packages("rmarkdown"); require("rmarkdown")}
```

<style type="text/css">
/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 14pt;
}
<!-- /* Headers */ -->
<!-- h1,h2,h3,h4,h5,h6{ -->
<!--   font-size: 24pt; -->
<!-- } -->
</style>

@@

## BEFORE PARTICIPANT ARRIVES:
- Devices
1. Connect the audio interface (Focusrite Scarlett 6i6) to Macbook Pro.
2. Connect twp headphones to the audio interface.
3. Connect the piano to the audio interface.
4. Turn on the piano, the audio interface and the screen in front of the piano.
5. Open “Focusrite Control” app ![](focusriteControl.jpg){ width=5% } and click “Load from device”.

![](01.png){ width=50% }
![](02.png){ width=80% }

@@

![](03.png){ width=80% }

@@

\pagebreak

@@

1. Go to Desktop >> Atsuko >> ExpertPiano >> open the “mainPatch.maxpat” and the “imageDisplay.maxpat”.
2. Move the window of the “imageDisplay.maxpat” to the right (on the screen in front of the piano”) and press F for a fullscreen mode.
3. Read the instruction for the “mainPatch.maxpat" below.
    + Start a trial with the space key.
    + Stop a trial with the Z key.
    + The blue patcher is used to change an image of the screen and start a metronome manually (mainly used for a practice session and instructions).
    + The green patcher shows ongoing recordings.
    + The yellow patcher shows the name of the current file.
    + The pink patcher (hidden) reads the condition of the current participant.

![](mainPatch_screen.png)

@@

![](inst_g1.png){ width=80% }

@@

![](stim_n.png){ width=80% }

@@

![](inst_g2.png){ width=80% }

@@

![](stim_a.png){ width=80% }

@@

![](inst_t.png){ width=80% }

@@

![](stim_d.png){ width=80% }

@@

![](stim_t.png){ width=80% }

@@

![](inst_p.png){ width=80% }

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.align = 'center')
# Install and load packages
if (!require("rmarkdown")) {install.packages("rmarkdown"); require("rmarkdown")}
```

<style type="text/css">
/* Whole document: */
body{
  font-family: Helvetica;
  font-size: 14pt;
}
</style>

@@

## BEFORE PARTICIPANT ARRIVES:
- Devices
1. Connect the audio interface (Focusrite Scarlett 6i6) to Macbook Pro.
2. Connect twp headphones to the audio interface.
3. Connect the piano to the audio interface.
4. Turn on the piano, the audio interface and the screen in front of the piano.
5. Open “Focusrite Control” app ![](./image/focusriteControl.jpg){ width=5% } and click “Load from device”.

![](./image/01.png){ width=50% }
![](./image/02.png){ width=80% }

@@

![](./image/03.png){ width=80% }

@@

@@

1. Go to Desktop >> Atsuko >> expertpiano >> open the “mainPatch.maxpat” and the “imageDisplay.maxpat”.
2. Move the window of the “imageDisplay.maxpat” to the right (on the screen in front of the piano”) and press F for a fullscreen mode.
3. Read the instruction for the “mainPatch.maxpat" below.
    + Start a trial with the space key.
    + Stop a trial with the Z key.
    + The blue patcher is used to change an image of the screen and start a metronome manually (mainly used for a practice session and instructions).
    + The green patcher shows ongoing recordings.
    + The yellow patcher shows the name of the current file.
    + The pink patcher (hidden) reads the condition of the current participant.

![](./image/mainPatch_screen.png)

@@

![](./image/inst_g1.png){ width=80% }

@@

![](./image/stim_n.png){ width=80% }

@@

![](./image/inst_g2.png){ width=80% }

@@

![](./image/stim_a.png){ width=80% }

@@

![](./image/inst_t.png){ width=80% }

@@

![](./image/stim_d.png){ width=80% }

@@

![](./image/stim_t.png){ width=80% }

@@

![](./image/inst_p.png){ width=80% }
